The Astropy Project

### 2017-10-18 main.tex
gwcs link

\subsection{Release cycle and Long Term Support}
% This could also include information about the development cycle
% Brigitta can writes this up if there's no other taker
\inlinecomment{BMS: TODO}{reference APE2 for versioning and APE10 for dropping python2 support}
\inlinecomment{BMS}{shall we maybe refer to the release calendar, too?}
\inlinecomment{BMS}{should we mention that v3.0 is the exception to the
  version numbering scheme we use by not being 2.1?}
%
\par The general scheme for the releases and version numbering that the core
package has adopted if the following. \astropypkg has new feature releases every
6 months, and between feature releases additional bugfix releases that
contain only bugfixes but no new features. The timing of
%
\par Long-term support (LTS) releases continue to receive bugfixes for 2
years with no changes to the API. They are ideal for pipelines and other
applications where API stability is essential. The latest LTS release is
also the last one that supports \python 2, and will receive bug fixes until the
end of 2019.
%
\par The version numbering of \astropypkg reflects on the release scheme
described above. The core package uses the form x.y.z, where x is advances
on LTS, y is advanced for a non-LTS feature release, and z is advanced on
bugfix releases.

@@

\subsection{Modeling}
\label{sec:modeling}
% The whole modeling submodule was missing from the previous paper, so everything really, including compound models, unit support etc.
% Nadia, Lim
% Tom R. -- unit support
\subsubsection{Overview}
The \package{astropy.modeling} subpackage provides a framework for representing analytical models and performing model evaluation and fitting. Models and fitters are independent of each other, a model can be fit with different fitters and new fitters can be added without changing existing models. The framework is designed to be flexible and easily extensible. The goal is to have a rich set of models but also make it easy to create new ones if necessary. The modeling framework is used in a variety of data analysis tools and is the basis for the Generalized World Coordinate System (GWCS) package (link). The unit support in models and fitters make it a unique package for working with astrophysical models.

>>>>

\subsection{Release cycle and Long Term Support}
% This could also include information about the development cycle
% Brigitta can writes this up if there's no other taker
\inlinecomment{BMS: TODO}{reference APE2 for versioning and APE10 for dropping python2 support}
\inlinecomment{BMS}{shall we maybe refer to the release calendar, too?}
\inlinecomment{BMS}{should we mention that v3.0 is the exception to the
  version numbering scheme we use by not being 2.1?}
%
\par The general scheme for the releases and version numbering that the core
package has adopted if the following. \astropypkg has new feature releases every
6 months, and between feature releases additional bugfix releases that
contain only bugfixes but no new features.
% The timing of
%
\par Long-term support (LTS) releases continue to receive bugfixes for 2
years with no changes to the API. They are ideal for pipelines and other
applications where API stability is essential. The latest LTS release is
also the last one that supports \python 2, and will receive bug fixes until the
end of 2019.
%
\par The version numbering of \astropypkg reflects on the release scheme
described above. The core package uses the form x.y.z, where x is advances
on LTS, y is advanced for a non-LTS feature release, and z is advanced on
bugfix releases.

@@

\subsection{Modeling}
\label{sec:modeling}
% The whole modeling submodule was missing from the previous paper, so everything really, including compound models, unit support etc.
% Nadia, Lim
% Tom R. -- unit support
\subsubsection{Overview}
The \package{astropy.modeling} subpackage provides a framework for representing
analytical models and performing model evaluation and fitting. Models and
fitters are independent of each other, a model can be fit with different
fitters and new fitters can be added without changing existing models. The
framework is designed to be flexible and easily extensible. The goal is to have
a rich set of models but also make it easy to create new ones if necessary. The
modeling framework is used in a variety of data analysis tools and is the basis
for the Generalized World Coordinate System (GWCS)
package\footnote{\url{https://github.com/spacetelescope/gwcs}}. The
unit support in models and fitters make it a unique package for working with
astrophysical models.
